MS&E 226: Project Part 1 Code

### 2024-12-03 MS&E 226_Project Part 2_Code.Rmd
ols model as chosen model

# 2: Data Pre-processing

@@

# 7: Classification

## Data Cleaning

@@

## 2: Inference

@@

# Print summary of the OLS regression model
summary(ols_train)

@@

#### (a)
```{r 2a}
# Extract the final Ridge model using the best lambda
final_ridge_model <- ridge_model$finalModel

# Extract coefficients from the final model
coefficients <- coef(final_ridge_model, s = final_lambda_ridge)

# Print the coefficients
print(coefficients)

@@

#### (b)
```{r}
# Select a subset of covariates
subset_column_names <- c(  "Demand.Summer.Peak", "Demand.Winter.Peak", "Sources.Generation", "Utility.Region", "Max.Revenue.Sector", "Revenue.Total", "Utility.Type")

@@

df_subset$Log_Revenue_Total <- log1p(df_subset$Revenue.Total)

# Train the Ridge Regression model using the subset of covariates
ridge_subset_model <- train(Log_Revenue_Total ~ ., 
                            data = df_subset, 
                            method = "glmnet",  
                            trControl = train_control,
                            metric = "RMSE", 
                            preProcess = "scale",  
                            tuneGrid = expand.grid(alpha = 0, lambda = seq(0, 1, length = 100)))

```
```{r}
# Get the coefficients for the best model at the selected lambda
best_lambda <- ridge_model$bestTune$lambda
best_model_coeffs <- coef(ridge_model$finalModel, s = best_lambda)

# Print all coefficients for the best Ridge Regression model
cat("All coefficients for the best Ridge Regression model:\n")
print(best_model_coeffs)

# Get coefficients for the subset model
best_lambda_subset <- ridge_subset_model$bestTune$lambda
best_model_coeffs_subset <- coef(ridge_subset_model$finalModel, s = best_lambda_subset)

# Print all coefficients for the subset model
cat("All coefficients for the Ridge Regression model with a subset of covariates:\n")
print(best_model_coeffs_subset)
```

>>>>

#Project Part 1

## 2. Data Pre-processing

@@

## 7. Classification

### Data Cleaning

@@

## 2. Inference

@@

# Print summary of the OLS regression model
ols_summary <- summary(ols_train)

@@

### Statistically Significant Coefficients
```{r 2a}
coefficients <- ols_summary$coefficients
print(coefficients)

# Extract and identify statistically significant coefficients (p-value < 0.05)
significant_coeffs <- coefficients[coefficients[, 4] < 0.05, ]

# Print the statistically significant coefficients and their p-values
print("Statistically significant coefficients:")
print(significant_coeffs)

# Now, let's extract the names of the statistically significant variables
significant_variable_names <- rownames(significant_coeffs)
print("Significant variables:")
print(significant_variable_names)

@@

### Subset of covariates model

```{r}
# Select a subset of covariates (as you did before)
subset_column_names <- c("Demand.Summer.Peak", "Demand.Winter.Peak", "Sources.Generation", "Utility.Region", "Max.Revenue.Sector", "Revenue.Total", "Utility.Type")

@@

# Create the log-transformed revenue variable
df_subset$Log_Revenue_Total <- log1p(df_subset$Revenue.Total)
df_subset$Revenue.Total <- NULL

# Create the formula for OLS regression
ols_formula <- as.formula(paste("Log_Revenue_Total ~", paste(subset_column_names[-6], collapse = " + ")))

# Train the OLS regression model
ols_model <- lm(ols_formula, data = df_subset)

# Print the summary of the OLS model
cat("OLS model coefficients summary:\n")
summary(ols_model)

# Extract and print the coefficients
cat("OLS model coefficients:\n")
print(coef(ols_model))

# Optional: Check the significance of each coefficient using the summary output
cat("OLS model coefficient significance:\n")
summary(ols_model)$coefficients[, 4]  # p-values of the coefficients

```{r}
# Get the summary of the OLS model
ols_summary <- summary(ols_model)

# Extract the p-values of the coefficients
p_values <- ols_summary$coefficients[, 4]

# Set a significance threshold (e.g., 0.05)
significance_threshold <- 0.05

# Identify significant coefficients based on p-value
significant_coeffs <- names(p_values)[p_values < significance_threshold]

# Print the significant coefficients
cat("Significant coefficients based on p-value < 0.05:\n")
print(significant_coeffs)
